Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-13 paper/paper.tex
update on the 1sigma test

As a test, we also run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
\mg{Is $1\sigma$ correct?}\jefr{What do you mean with
  that question?}
Consistent with the results from the random forest algorithm,
illustrated by the classification tree of Figure \ref{fig:tree},

Having constrained only 3 parameters, one might wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading because merely the best-fit values of (some of) those $3$ parameters, i.e., the corresponding constraint to a given sub-region in the parameter space, make the other parameters less important.
For instance, in our case the large value of $P_{\rm cl}$ makes radiative transfer effects, and therefore other parameters such as the clump column density less relevant for the emergent line profile. However, for instance larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce additional radiative transfer effects and thus increase the number of relevant parameters \citep[see ][for details]{2017arXiv170406278G}. 
This means that even
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected,
\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
i.e. we cannot randomly pick 11 random values for these
parameters and expect to fit the line profile while only varying the
other 3

>>>>

As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is we have a $30\%$ chance to find good models compared with the
lower $1\%$ success rate if the parameters were unconstrained. 
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $1\sigma$. All the other parameters were unconstrained.}

Having constrained only 3 parameters one might wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading because merely the best-fit values of
(some of) those $3$ parameters, i.e., the corresponding constraint to
a given sub-region in the parameter space, make the other parameters
less important. 
For instance, in our case the large value of $P_{\rm cl}$ makes
radiative transfer effects, and therefore other parameters such as the
clump column density less relevant for the emergent line
profile. However, for instance larger values of $f_{\rm cl}$ --
outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected,
\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
i.e. we cannot randomly pick 11 random values for these
parameters and expect to fit the line profile while only varying the
other 3
